Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2016-06-19 LaTeX/response.tex

  \item Page 3, line -2: \ldots compared TO Gaussian AND max-stable \ldots \\

  \begin{response}
    This has been corrected
  \end{response}

  \item Page 8, line -1: a partition in the $\bw^∗$ space induces a partition in the $\bw^∗$. The property (7) is used in the $\bw^∗$ space. Is this property still respected in the $\bw$ space since the transformation is non-linear and acts independently in each coordinate? \\

  \begin{response}
    When we create the partition, it is created in the space of the original data (i.e. using $\bw$).
    As you mention, because the transformation is non-linear and acts independently in each coordinate, the partition created using $\bw$ will be similar to, but not the same as the partition created using $\bw^*$.
    We have added clarification in \sref{sts:temporal} to clarify that the partition is created in the $\bw$ space as opposed to the $\bw^*$ space.
    % \hl{Is this something we should be concerned about?}
  \end{response}

@@

\end{enumerate}

\newpage
\section*{Response to the comments of the Reviewer 1}

\subsection*{Major comments}
\begin{enumerate}[1.]
  \item The overall modeling goal is never fully clear. In the abstract you write ``We present a new method based on the spatial skew-t process.'' But a new method for what? Reading the paper there are hints that you the aim of the modeling procedure might be to predict the probability of exceeding 75ppb (e.g. first line of the abstract), but this is then taken as one of your modeling thresholds (p.3 l.5--6; p. 15 l.5). In a new version of the paper, the modeling aims should be stated clearly upfront so that the results can be assessed against these aims. \\

  \begin{response}
    As we now describe at the end of the first paragraph of the introduction, two objectives for our data analysis are spatial prediction and mapping the probability of an extreme event.
    In the extremes context, spatial prediction means using the values of monitored stations to determine whether an unmonitored site experienced an extreme event.
    Mapping the probability of extreme events could either be the marginal probability of an event, such as ozone exceeding 75ppb, or a map of an upper quantile, such as the map of the 99th percentile in \fref{stfig:ozoneq99}.
  \end{response}

### 2016-06-19 LaTeX/skewt_rev.tex
manuscript updates for revision submission

The partitioning model remove long-range dependence. Conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs_1$ and $\bs_2$ in partitions $k_1$ and $k_2$ respectively is
\begin{align}
  \chi(h) &= I(k_1 = k_2) \chi_{\text{skew-}t}(h) + I(k_1 \neq k_2) \chi_{\text{Gaus}}(h) \nonumber \\
         &= I(k_1 = k_2) \chi_{\text{skew-}t}(h) \label{steq:chiskewt}
\end{align}
where $I(\cdot)$ is an indicator function, $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a skew-$t$ process given in equation \eref{steq:chiskew-t} of \aref{sta:skewt}, $\chi_{\text{Gaus}}(h)$ is the $\chi$ statistic for a Gaussian process, and $h = ||\bs_1 - \bs_2||$.
Therefore, sites in different subregions are asymptotically independent because $\chi_{\text{Gaus}}(h) = 0$ for all $h$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_1 = k_2)$ is the probability that two sites separated by distance $h$ are in the same partition.
In \aref{sta:proofsamepartition}, we show that $\lim_{h \rightarrow \infty} \pi(h) = 0$, assuming that the knots follow a homogeneous Poisson process.
This implies that $\lim_{h \rightarrow \infty} \chi(h) = 0$.
In practice we fix $K$ at a finite value and use a uniform distribution for the knots $\bw_1, \ldots, \bw_K$.
In \fref{stfig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a skew-$t$ distribution with $\alpha = 10$, and 3 degrees of freedom.
In \fref{stfig:chi} we estimate $\pi(h)$ through simulation.
% To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
% We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
% For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
% This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.

@@

$M = 50$ data sets are generated for each design.
For each data set we fit the data using six models
\begin{enumerate}[leftmargin=3em]
  \item Gaussian marginal, $K=1$ knots
  \item Skew-$t$ marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item Skew-$t$ marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
  \item A max-stable model based on \citet{Reich2012} thresholded at $T = q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
All methods are fit using a fully-Bayesian approach that simultaneously estimates marginal and spatial dependence parameters.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$ although only the intercept is used in the data generation.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\varphi \sim \text{Unif}(15)$.
The skewness parameter has prior $\lambda \sim N(0, 20)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(a / 2, b / 2)$, where $a$ has a discrete uniform prior on a mesh from $0.2$ to $20$ with spacing of $0.1$ and $b$ has a Gamma$(0.1, 0.1)$ prior.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We tried also fitting the skew-$t$ marginals for the thresholded models, but it is very challenging for the MCMC to properly identify the skewness parameter with a censored left tail.
Each chain of the MCMC ran for 20,000 iterations with a burn-in period of 10,000 iterations.
Although the goal of this simulation study is not to assess parameter estimation, for design (2) and method (2), the $\lambda$ estimate and and $a$ appear to converge to their true values (96\% coverage and 90\% coverage respectively).
It should be noted that in the models with multiple partitions (i.e. models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC; however, we are not interested in these parameters but rather spatial predictions and tail probabilities which converge well.

>>>>

The partitioning model removes long-range dependence. Conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs_1$ and $\bs_2$ in partitions $k_1$ and $k_2$ respectively is
\begin{align}
  \chi(h) &= I(k_1 = k_2) \chi_{\text{skew-}t}(h) \label{steq:chiskewt}
\end{align}
where $I(\cdot)$ is an indicator function, $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a skew-$t$ process given in equation \eref{steq:chiskew-t} of \aref{sta:skewt}, and $h = ||\bs_1 - \bs_2||$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_1 = k_2)$ is the probability that two sites separated by distance $h$ are in the same partition.
In \aref{sta:proofsamepartition}, we show that $\lim_{h \rightarrow \infty} \pi(h) = 0$, assuming that the knots follow a homogeneous Poisson process.
This implies that $\lim_{h \rightarrow \infty} \chi(h) = 0$.
In practice we fix $K$ at a finite value and use a uniform distribution for the knots $\bw_1, \ldots, \bw_K$.
In \fref{stfig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a skew-$t$ distribution with $\alpha = 10$, and 3 degrees of freedom.
In \fref{stfig:chi} we estimate $\pi(h)$ through simulation.
% To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
% We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
% For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
% This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.

@@

$M = 50$ data sets are generated for each design.
For each data set we fit the data using six models
\begin{enumerate}[leftmargin=3em]
  \item Gaussian marginal, $K=1$ knots
  \item Skew-$t$ marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item Skew-$t$ marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
  \item A max-stable model based on \citet{Reich2012} thresholded at $T = q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
All methods are fit using a fully-Bayesian approach that simultaneously estimates marginal and spatial dependence parameters.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$ although only the intercept is used in the data generation.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\varphi \sim \text{Unif}(15)$.
The skewness parameter has prior $\lambda \sim N(0, 20)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(a / 2, b / 2)$, where $a$ has a discrete uniform prior on a mesh from $0.2$ to $20$ with spacing of $0.1$ and $b$ has a Gamma$(0.1, 0.1)$ prior.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We tried also fitting the skew-$t$ marginals for the thresholded models, but it is very challenging for the MCMC to properly identify the skewness parameter with a censored left tail.
Each chain of the MCMC ran for 20,000 iterations with a burn-in period of 10,000 iterations.
Although the goal of this simulation study is not to assess parameter estimation, for design (2) and method (2) where data are generated and fit with a skew-$t$ distribution, the sample converges for $\lambda$ and $a$, and the empirical coverage of posterior 95\% intervals is near the nominal level (96\% coverage for $\lambda$ and 90\% for $a$).
It should be noted that in the models with multiple partitions (i.e. models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC; however, we are not interested in these parameters but rather spatial predictions and tail probabilities which converge well.

### 2016-06-19 LaTeX/supplemental_rev.tex
manuscript updates for revision submission

\section{Temporal dependence} \label{sta:temporal}
It is very challenging to derive an analytical expression the temporal extremal dependence at a single site $\bs$.
However, using simulated data, we have evidence to suggest that the model does exhibits temporal extremal dependence.
To demonstrate that our model maintains temporal extremal dependence, we generate lag-$m$ observations for $m = 1, 3, 5, 10$ from our model setting $\phi_w = \phi_z = \phi_\sigma = \varphi$, for $\varphi = 0, 0.02, 0.04, \ldots, 1$.
To estimate the lag-$m$ chi-statistic $\chi(m)$ we first estimate the lag-$m$ $F$-madogram $\nu_F(m)$ \citep{Cooley2006} using $\hat{\nu}_F(m) = \frac{1}{2n} \sum_{i = 1}^n | \hat{F}(y_{0}) - \hat{F}(y_{m})|$ where $\hat{F}(\cdot)$ represents an empirical CDF and $y_m$ is the lag-$m$ observation.
The $F$-madogram is related to the $\chi$ statistic as follows
\begin{align}
  \chi = 2 - \frac{1 + 2 \nu_F}{1 - 2 \nu_F}.
\end{align}
\fref{stfig:chiphi} suggests that the extremal dependence increases as $\phi \rightarrow 1$, and that the extremal dependence decreases as $m$ increases.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{plots/chi-phi}
  \caption{Simulated lag-$m$ $\chi$ for varying levels of $\varphi$.}
  \label{stfig:chiphi}
\end{figure}

>>>>

\section{Temporal dependence} \label{sta:temporal}
It is very challenging to derive an analytical expression the temporal extremal dependence at a single site $\bs$.
However, using simulated data, we have evidence to suggest that the model does exhibits temporal extremal dependence.
To demonstrate that our model maintains temporal extremal dependence, we generate lag-$m$ observations for $m = 1, 3, 5, 10$ from our model setting $\phi_w = \phi_z = \phi_\sigma = \varphi$, for $\varphi = 0, 0.02, 0.04, \ldots, 1$.
To estimate the lag-$m$ chi-statistic $\chi(m)$ we first estimate the lag-$m$ $F$-madogram $\nu_F(m)$ \citep{Cooley2006} using $\hat{\nu}_F(m) = \frac{1}{2n} \sum_{i = 1}^n | \hat{F}(y_{0}) - \hat{F}(y_{m})|$ where $\hat{F}(\cdot)$ represents an empirical CDF and $y_m$ is the lag-$m$ observation.
The $F$-madogram is related to the $\chi$ statistic as follows
\begin{align}
  \chi = 2 - \frac{1 + 2 \nu_F}{1 - 2 \nu_F}.
\end{align}
\fref{stfig:chiphi} suggests that the extremal dependence increases as $\varphi \rightarrow 1$, and that the extremal dependence decreases as $m$ increases.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{plots/chi-phi}
  \caption{Simulated lag-$m$ $\chi$ for varying levels of $\varphi$.}
  \label{stfig:chiphi}
\end{figure}
